Self-test prime dimensional EPR pairs with constant alphabet

### 2019-02-01 Draft/draft.tex
Honghao: minor changes

The case of self-testing $2$-dimensional EPR pair is fully understood. One can robustly self-test
one copy of it by the CHSH inequality \cite{bamps2015}. and self-test many copies of the $2$-dimensional EPR
pair in parallel \cite{mckague2016, coladan2017parallel}. 
Self-testing general $d$-dimensional EPR pairs is a harder task.
Recently, a remarkable result by Coladangelo \textit{et al}.\cite{cgs2017} 
has shown that the maximally entangled state with arbitrary local dimension 
can be self-tested with constant question alphabet but answer alphabet growing with
the local dimension. 
Then Coladangelo and Stark \cite{coladan2017} further showed that by playing many instances
of the generalized Magic Square game and Magic Pentagram game, one can self-test
$N$ copies of the maximally entangled state with local dimension $d$ for any $d, N \geq 2$.
Both the Magic Square game and the Magic Pentagram game have constant question alphabet
but growing answer alphabet.

In summary, general $d$-dimensional maximally entangled states are self-tested by
modifying the correlation and enlarging the size of the correlation.
A natural question to ask is whether maximally entangled state with large local dimension
can be self-tested with fixed-sized correlation. 
An equivalent question to ask is whether it is possible to self-test maximally
entangled state more efficiently, with constant question and answer set. 
In this report, we give an affirmative answer to this question by proving the following theorem.
\begin{theorem}[Informal]
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $d-1$ can be self-tested 
	with constant-sized question and answer alphabets.
\end{theorem}

The set $D$ is easily characterizable as it contains all the odd prime numbers with 
primitive root $2$, $3$ or $5$. It has been shown that there are infinitely many prime numbers
with primitive root in the set $\{2,3,5\}$ \cite{murty1988}, so the set $D$ has infinitely many elements.
To prove \cref{thm:inf}, we give explicit self-testing proof of 
the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$,$3$, or $5$, 
by explicitly giving the correlation that achieves self-testin. 
%Then the self-testing property of this correlation is 
%given in the following theorem.
%\begin{theorem}[Informal]
%\label{thm:pr_2}
%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
%\end{theorem}
Our correlation is denoted by $C(\dr{r})$ for prime $d$.
We use the superscript $(r)$ to denote the primitive root of $d$.
Note that although the size of $C(\dr{r})$ does not depend on $d$, the optimal correlation does.

In order to accomplish our goal, we introduce new techniques for self-testing.
First of all, we use a different variant of the weighted CHSH inequality to enforce the eigenvalue of
some unknown operator which is decomposed into two binary observables.
The variant of the CHSH inequality that we use is not used in the self-testing literature befor.
Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintain
certain commutation relations. Such decomposition is different from what Slofstra used in his work \cite{slofstra2017}.
Intuitively, such decomposition can be seen as the inverse of the decomposition used in the proof of Jordan's lemma.
The third contribution is that we prove self-testing without using anti-commutation relations between Pauli operators, 
which is the core idea in all the previous self-testing results. 
Instead, we find a new pair of operators that can generate the ring of matrices over complex numbers.

\textbf{Structure of the paper}.
We start with notations and background information in \cref{sec:prelim}.
Since the correlation we designed satisfies two sub-tests, we introduce one test
in \cref{sec:lsg} and the other one in \cref{sec:chsh}. Our main result is based on the combination
of the sub-tests and presented in \cref{sec:main}.

@@

We use some basic number theory concepts in our work. A primitive root of a prime number
$d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
$r$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$ where
$\Z_d^\times = \{1,2\dots d-1\}$.
The EPR pair of local dimension $d-1$ for some prime $d$ is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{i = 0}^{d-2} \ket{ii}.
\end{align}
The superscript $(d-1)$ stresses the local dimension and we follow this convention through this paper.

@@

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 1,2$ 
on Hilbert space $\calH_A$ and $\calH_B$ respectively.
A binary observable is a Hermitian matrix whose only eigenvalues are either $+1$ or $-1$.
The weighted CHSH inequality is given by 
\begin{align}
	\label{eq:chsh_op}
	\I_\alpha = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
\end{align}
where $\ip{A_xB_y}$ is the expectation value of of the observables.
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \I_\alpha \leq 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy for $\I_\alpha$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
measurements, which is a phenomenon referred as a self-test. We give formal statement of this self-testing result in \cref{sec:chsh}.

@@

The main contribution of our work is the construction of a correlation, which is the optimal correlation of a nonlocal game $\G$ with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
such that this correlation can self-test $\ket{\EPR{d-1}}$ for arbitrary $d \in D$. 
The nonlocal game $\G$ is a linear system game with strict enforcements. 
We introduce the definition of self-testing, the definition of linear system game, 
and its operator solution, 
following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
\begin{definition}[Self-testing]
	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
	such that 	
	\begin{align*}
		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
	\end{align*}
\end{definition}
\begin{definition}[Linear system game]
 Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
 that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
 Formally, the winning condition is 
 \begin{align*}
 	a(j) &= b && \text{(Consistency)} \\
	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
 \end{align*}
 for all $(i,j) \in \calX \times \calY$.
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.
We focus on quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy for the linear system game $(Hx = c)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement, and
vice versa.

It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
operator solution in the following sense.
\begin{definition}[Operator solution of a linear system]
\label{def:op_sol}
	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of bounded Hermitian 
	operators $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that 
	\begin{enumerate}
		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
		\item for all $1 \leq i \leq m$,
		\begin{align*}
			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
		\end{align*}
	\end{enumerate}
	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
	solution in which the Hilbert space is finite-dimensional.
\end{definition}
Perfect quantum strategies can be extracted from operator solutions and vice versa.

Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
over $\Z_2$, which is called the solution group.
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,c) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
For concepts about group presentation, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
Combining \cref{def:op_sol} and \cref{def:presentation}, we know that an operator solution associated to $Hx =c$ is 
a finite-dimensional representation of $\Gamma(H,c)$ that maps $J$ to $-\1$.

>>>>

The case of self-testing $2$-dimensional EPR pair is fully understood. One can robustly self-test
one copy of it by the CHSH inequality \cite{bamps2015}. and self-test many copies of the $2$-dimensional EPR
pair in parallel \cite{mckague2016, coladan2017parallel}. 
Self-testing general $d$-dimensional EPR pairs is a harder task.
Recently, a remarkable result by Coladangelo \textit{et al}.\cite{cgs2017} 
has shown that the maximally entangled state with arbitrary local dimension 
can be self-tested with constant question alphabet but answer alphabet growing with
the local dimension. 
Then Coladangelo and Stark \cite{coladan2017} further showed that by playing many instances
of the generalized Magic Square game and Magic Pentagram game, one can robustly self-test
$N$ copies of the maximally entangled state with local dimension $d$ for any $d, N \geq 2$.
Both the Magic Square game and the Magic Pentagram game have constant question alphabet
but answer alphabet of size $d$.

At a high level, general $d$-dimensional maximally entangled states are self-tested by
modifying the correlation and enlarging the size of the correlation.
A natural question to ask is whether maximally entangled state with large local dimension
can be self-tested with fixed-sized correlation. 
An equivalent question to ask is whether it is possible to self-test maximally
entangled state of some local dimension more efficiently, with constant correlation size. 
In this report, we give an affirmative answer to this question by proving the following theorem.
\begin{theorem}[Informal]
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $d-1$ can be self-tested 
	with constant-sized question and answer alphabets.
\end{theorem}

The set $D$ is easily characterizable as it contains all the odd prime numbers with smallest
primitive root $2$, $3$ or $5$. It has been shown that there are infinitely many prime numbers
with smallest primitive root in the set $\{2,3,5\}$ \cite{murty1988}, so the set $D$ has infinitely many elements.
To prove \cref{thm:inf}, we give explicit self-testing proof of 
the maximally entangled state with local dimension $d-1$ where the primitive root of $d$ is $2$,$3$, or $5$, 
by explicitly giving the correlation that achieves self-testing. 
%Then the self-testing property of this correlation is 
%given in the following theorem.
%\begin{theorem}[Informal]
%\label{thm:pr_2}
%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
%\end{theorem}
Our correlation is denoted by $C(\dr{r})$ for prime $d$.
We use the superscript $(r)$ to denote the primitive root of $d$.
Note that although the size of $C(\dr{r})$ does not depend on $d$, the optimal correlation does.

In order to accomplish our goal, we introduce new techniques for self-testing.
First of all, we use a different variant of the weighted CHSH inequality to enforce the eigenvalue of
some unknown operator which is the product of two binary observables used in the weighted CHSH test.
The variant of the CHSH inequality that we use is not used in the self-testing literature before.
Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintains
certain commutation relations. Such decomposition is different from what Slofstra used in his work \cite{slofstra2017}.
Intuitively, such decomposition can be seen as the inverse of the Jordan's lemma decomposition.
The third contribution is that we prove self-testing without using anti-commutation relations between Pauli operators, 
which is the core idea in all the previous self-testing results. 
Instead, we find a new pair of operators that can generate the ring of matrices over complex numbers.

\textbf{Structure of the paper}.
We start with notations and background information in \cref{sec:prelim}.
Since the correlation we designed can win a special linear system game and satisfy
an extended weighted CHSH test, we introduce the linear system game
in \cref{sec:lsg} and the extended weighted CHSH test in \cref{sec:chsh}. 
Our main result is based on the combination of the two tests and presented in \cref{sec:main}.

@@

We use some basic number theory in our work. A primitive root of a prime number
$d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
$r$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$ where
$\Z_d^\times = \{1,2\dots d-1\}$. When we say $d$ has primitive root $r$, we always mean
that $r$ is the smallest primitive root.

The EPR pair of local dimension $d-1$ for some prime $d$ is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{i = 0}^{d-2} \ket{ii}.
\end{align}
The superscript $(d-1)$ stresses the local dimension and we follow this convention through this paper.

@@

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 1,2$ 
on Hilbert space $\calH_A$ and $\calH_B$ respectively.
A binary observable is a Hermitian matrix whose only eigenvalues are either $+1$ or $-1$.
The weighted CHSH inequality is given by 
\begin{align}
	\label{eq:chsh_op}
	\I_\alpha = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
\end{align}
where $\ip{A_xB_y}$ is the expectation value of of the observables.
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \I_\alpha \leq 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy for $\I_\alpha$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
measurements up to isometry, 
which is a phenomenon referred as a self-test. We give formal statement of this self-testing result in \cref{sec:chsh}.

@@

The main contribution of our work is the construction of a correlation, which is the combination of 
the optimal correlation of a linear system game with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
and the optimal correlation to violate the weighted CHSH inequality.
The special property of the correlation is that it can self-test $\ket{\EPR{d-1}}$ for arbitrary $d$ with certain 
primitive root. 
In the next part, we introduce the definition of self-testing, the definition of linear system game, 
and its operator solution, 
following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
\begin{definition}[Self-testing]
	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
	such that 	
	\begin{align*}
		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
	\end{align*}
\end{definition}
\begin{definition}[Linear system game]
 Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
 that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
 Formally, the winning condition is 
 \begin{align*}
 	a(j) &= b && \text{(Consistency)} \\
	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
 \end{align*}
 for all $(i,j) \in \calX \times \calY$.
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.
We focus on quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy for the linear system game $(Hx = c)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement, and
vice versa.

It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
operator solution in the following sense.
\begin{definition}[Operator solution of a linear system]
\label{def:op_sol}
	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of bounded Hermitian 
	operators $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that 
	\begin{enumerate}
		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
		\item for all $1 \leq i \leq m$,
		\begin{align*}
			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
		\end{align*}
	\end{enumerate}
	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
	solution in which the Hilbert space is finite-dimensional.
\end{definition}
Perfect quantum strategies can be extracted from operator solutions and vice versa.
Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
over $\Z_2$, which is called the solution group.
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,c) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
For concepts about group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
Combining \cref{def:op_sol} and \cref{def:presentation}, we know that an operator solution associated to $Hx =c$ is 
a finite-dimensional representation of $\Gamma(H,c)$ that maps $J$ to $-\1$.
